Demographic Species Distribution Models

### 2019-12-02 manuscript/ms.Rmd
fix equations

\begin{align}
y_i &\sim Bernoulli(p_i) \\ \nonumber
p_i &= 1 - e^{-\Lambda_i} \\ \nonumber
\Lambda_i &= ln(1 + e^{K_i})  \\ \nonumber
K_i &= (\lambda_i - 1) \alpha \\ \nonumber
\lambda_i &= eigval(\mathbf{A_i})
\end{align}

@@

\begin{align}
\beta_{F} &\sim N(\mu_F, \mathbf{\Sigma}_F) \\ \nonumber
\beta_{S} &\sim N(\mu_S, \mathbf{\Sigma}_S) \\ \nonumber
\gamma &\sim N(1.17, 2.10) \\ \nonumber
alpha &\sim U(0, \infty)
\end{align}.

The spatially-averaged fecundity and adult survival estimates from @ryuDevelopingPopulationModels2016 were used to define priors on regression coefficients for the vital rate submodels. These estimated vital rates correspond to populations at the $J$ survey stations used in the recapture analysis (station names provided in the supplemental data to @ryuDevelopingPopulationModels2016) - locations where the species occurs. I defined a prior on $\beta_F$ and $\beta_S$ such that values were *a priori* more likely if they resulted in estimates of $F_j$ and $S_{A_j}$, for each survey station location $j$, that were more consistent with the estimates in @ryuDevelopingPopulationModels2016.
First, the means and variances of these estimates were used to calculate equivalent parameters of univariate normal distributions on the link-scale of the regression submodels, resulting in the implied priors: $ln(F_j) \sim N(-0.63, 0.18)$, $logit(S_{A_j}) \sim N(1.12, 1.28)$, and $logit(S_{J_j}) \sim N(-0.05, 0.85)$.
These normally-distributed implied priors correspond exactly to multivariate normal priors on the vectors of regression coefficients, since the matrix-multiplication that maps between regression coefficients and link-scale response is an affine transformation, under which the multivariate normal distribution is closed. The parameters of the priors over $\beta_F$ are therefore given by: $\mu_F = \mathbf{X}_*^{-1}(\text{-}0.63\, \mathbf{I})$ and $\mathbf{\Sigma} = \mathbf{X}_*^{-1} (0.18\,\mathbf{I}) \mathbf{X}_*^{-T}$, where $\mathbf{X}_*$ denotes the design matrix over the $J$ survey stations, $\mathbf{X}_*^{-1}$ its Moore-Penrose pseudoinverse, $\mathbf{X}_*^{-T}$ the transpose of that pseudoinverse, and $\mathbf{I}$ an identity matrix of dimension $J$. The prior parameters $\mu_S$ and $\mathbf{\Sigma}_S$ were defined in the same way using the implied prior parameters over $logit(S_{A_j})$: 1.12, and 1.28.
Note that these priors do not provide any information on the direction of the relationships between vital rates and environmental covariates (the intercept elements of $\mu_F$ and $\mu_S$ are informed, but the prior mean for the other terms is $\approx 0$), but by providing information on plausible magnitudes of, and correlations between these parameters the prior favours regression equations that pass close to the vital rate estimates at $F_j$ and $S_j$.
The prior for $\gamma$, the logit-difference between adult and juvenile survival, is given by the difference between the implied normal priors on logit-survival of adults and juveniles, which is also normal.
In the absence of any meaningful prior information for the competition effects or detection rates, I assigned $\alpha$ an improper uniform prior on all positive values.

>>>>

\begin{align}
y_i &\sim Bernoulli(p_i) \\ \nonumber
p_i &= 1 - e^{-\Lambda_i} \\ \nonumber
\Lambda_i &= ln(1 + e^{K_i})  \\ \nonumber
K_i &= (\lambda_i - 1) \alpha \\ \nonumber
\lambda_i &= eigval(\mathbf{A}_i)
\end{align}

@@

\begin{align}
\beta_{F} &\sim N(\mu_F, \mathbf{\Sigma}_F) \\ \nonumber
\beta_{S} &\sim N(\mu_S, \mathbf{\Sigma}_S) \\ \nonumber
\gamma &\sim N(1.17, 2.10) \\ \nonumber
\alpha &\sim U(0, \infty)
\end{align}.

The spatially-averaged fecundity and adult survival estimates from @ryuDevelopingPopulationModels2016 were used to define priors on regression coefficients for the vital rate submodels. These estimated vital rates correspond to populations at the $J$ survey stations used in the recapture analysis (station names provided in the supplemental data to @ryuDevelopingPopulationModels2016) - locations where the species occurs. I defined a prior on $\beta_F$ and $\beta_S$ such that values were *a priori* more likely if they resulted in estimates of $F_j$ and $S_{A_j}$, for each survey station location $j$, that were more consistent with the estimates in @ryuDevelopingPopulationModels2016.
First, the means and variances of these estimates were used to calculate equivalent parameters of univariate normal distributions on the link-scale of the regression submodels, resulting in the implied priors: $ln(F_j) \sim N(-0.63, 0.18)$, $logit(S_{A_j}) \sim N(1.12, 1.28)$, and $logit(S_{J_j}) \sim N(-0.05, 0.85)$.
These normally-distributed implied priors correspond exactly to multivariate normal priors on the vectors of regression coefficients, since the matrix-multiplication that maps between regression coefficients and link-scale response is an affine transformation, under which the multivariate normal distribution is closed. The parameters of the priors over $\beta_F$ are therefore given by: $\mu_F = \mathbf{X}_*^{-1}(\text{-}0.63\, \mathbf{I})$ and $\mathbf{\Sigma}_F = \mathbf{X}_*^{-1} (0.18\,\mathbf{I}) \mathbf{X}_*^{-T}$, where $\mathbf{X}_*$ denotes the design matrix over the $J$ survey stations, $\mathbf{X}_*^{-1}$ its Moore-Penrose pseudoinverse, $\mathbf{X}_*^{-T}$ the transpose of that pseudoinverse, and $\mathbf{I}$ an identity matrix of dimension $J$. The prior parameters $\mu_S$ and $\mathbf{\Sigma}_S$ were defined in the same way using the implied prior parameters over $logit(S_{A_j})$: 1.12, and 1.28.
Note that these priors do not provide any information on the direction of the relationships between vital rates and environmental covariates (the intercept elements of $\mu_F$ and $\mu_S$ are informed, but the prior mean for the other terms is $\approx 0$), but by providing information on plausible magnitudes of, and correlations between these parameters the prior favours regression equations that pass close to the vital rate estimates at $F_j$ and $S_j$.
The prior for $\gamma$, the logit-difference between adult and juvenile survival, is given by the difference between the implied normal priors on logit-survival of adults and juveniles, which is also normal.
In the absence of any meaningful prior information for the competition effects or detection rates, I assigned $\alpha$ an improper uniform prior on all positive values.
